---
output:
  pdf_document:
    latex_engine: xelatex
geometry: margin=0.2in
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = "/home/glennrdx/Documents/lab_projects/microenvironments/02_output/") })
---

# Load Packages

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_knit$set(root.dir = "/home/glennrdx/Documents/lab_projects/microenvironments/01_data/")

# Load libraries
library(tidyverse, quietly = T) # CRAN
library(Matrix, quietly = T) # CRAN
library(ggplot2, quietly = T) # CRAN
library(data.table, quietly = T) # CRAN
library(Seurat, quietly = T) # CRAN
library(dplyr, quietly = T) # CRAN
library(viridis, quietly = T) # CRAN
library(sctransform, quietly = T) # CRAN
library(RANN, quietly = T) # CRAN
library(ggrastr, quietly = T) # CRAN
library(paletteer)
library(scry, quietly = T) # bioconductor
library(SingleCellExperiment, quietly = T) # bioconductor
```

# Load Data

```{r}
iss_expr <- readRDS("janesick_2023/raw_clean/iss_expr_clean.RDS")
iss_meta <- readRDS("janesick_2023/raw_clean/iss_meta_clean.RDS")
```

### Goal:  
For each invasive tumour cell, determine the percentage neighbours within the defined radius are either of the two types: Prolif_Invasive_Tumor/Invasive_Tumor (i.e. what percentage are tumourous, remaining percentage are other cell types).  

### Method:  
#### Step 1 - create spatial graph:  
Define radius size R  
Iterate over each cell:  
  - every other cell found within the circle of radius R is now connected to index cell.  

#### Step 2 - calculate neighbourhood composition of Invasive_Tumor cells:  
For each Invasive_Tumor cell:  
  - Calculate the percentage of neighbours that are either Invasive_Tumor or Prolif_Invasive_Tumor.  
  - If The percentage is 90% or more, classify the Invasive_Tumor cell as "Core", otherwise "Surface".  

```{r, fig.width=7.87, fig.height = 6.5, dpi=300, dev='tiff', out.width='100%'}
# Parameters
R <- 25  # Radius for neighborhood definition
threshold <- 0.90  # Threshold for Core vs Surface classification

# Create circle coordinates
circle <- data.frame(
  x = 3000 + R * cos(seq(0, 2*pi, length.out = 500)),
  y = 2000 + R * sin(seq(0, 2*pi, length.out = 500))
)

# Plot to visualise the radius of the circle
ggplot(iss_meta, aes(x = x_centroid, y = y_centroid)) +
  geom_point(color = "grey", size = 0.01, alpha = 0.8, shape = '.') +
  geom_path(data = circle, aes(x = x, y = y), color = "black", linewidth = 0.3) +
  scale_x_reverse() +
  coord_fixed() +
  guides(color = guide_legend(override.aes = list(shape = 16, size = 3))) +
  theme_minimal() +
  theme(
    legend.position = "bottom", 
    legend.box = "horizontal", 
    legend.margin = margin(0, 0, 0, 0), 
    plot.margin = margin(0, 0, 0, 0, "pt")
  )

```
  
```{r}
iss_meta <- data.table(
  cell_id = iss_meta$cell_id,
  x_centroid = iss_meta$x_centroid,
  y_centroid = iss_meta$y_centroid,
  Annotation = iss_meta$Annotation
)
coords <- iss_meta[, .(x_centroid, y_centroid)]

radius <- 50

# Perform radius search
nn_result <- nn2(data = coords, query = coords, searchtype = "radius", radius = radius)

adj_list <- vector("list", nrow(iss_meta))
names(adj_list) <- iss_meta$cell_id

for (i in 1:nrow(iss_meta)) {
  neighbor_idx <- nn_result$nn.idx[i, ]
  neighbor_idx <- neighbor_idx[neighbor_idx != 0 & neighbor_idx != i]  # remove 0s and self
  adj_list[[i]] <- iss_meta$cell_id[neighbor_idx]
}

target_cells <- iss_meta[Annotation %in% c("Invasive_Tumor", "Prolif_Invasive_Tumor"), cell_id]

core_surface <- data.table(cell_id = target_cells, Classification = NA_character_)

for (i in seq_along(target_cells)) {
  cell <- target_cells[i]
  neighbors <- adj_list[[as.character(cell)]]
  
  if (length(neighbors) == 0) {
    core_surface[i, Classification := "Surface"]
    next
  }
  
  num_target_neighbors <- sum(neighbors %in% target_cells)
  fraction <- num_target_neighbors / length(neighbors)
  
  if (fraction > 0.9) {
    core_surface[i, Classification := "Core"]
  } else {
    core_surface[i, Classification := "Surface"]
  }
}
```

```{r}
iss_meta <- merge(iss_meta, core_surface, by = "cell_id", all.x = TRUE)
iss_meta[, surface_class_radius := ifelse(is.na(Classification), "Other", Classification)]
```

```{r}
table(iss_meta$surface_class_radius)
```

```{r}
# Make Seurat object with ISS data
iss_obj <- CreateSeuratObject(counts = iss_expr, meta.data = iss_meta)

# filter to invasive cells only
iss_obj_invasive <- subset(iss_obj, subset = Annotation %in% 'Invasive_Tumor')
saveRDS(iss_obj_invasive, file = "janesick_2023/processed/iss_obj_invasive.RDS")
```

# Plot
```{r, fig.width=7.87, fig.height = 6.5, dpi=300, dev='tiff', out.width='100%'}
ggplot(iss_meta, aes(x = x_centroid, y = y_centroid)) +
  geom_point(aes(color = surface_class_radius), size = 0.01, alpha = 0.8, shape = '.') +
  scale_color_manual(values = c("Surface" = "#C90065", "Core" = "#fac0da", "Other" = "grey75"), na.value = "grey75") +
  scale_x_reverse() +
  coord_fixed() +
  guides(color = guide_legend(override.aes = list(shape = 16, size = 3))) +
  theme_minimal() +
  theme(
    legend.position = "bottom", 
    legend.box = "horizontal", 
    legend.margin = margin(0, 0, 0, 0), 
    plot.margin = margin(0, 0, 0, 0, "pt")
    )
```