---
output:
  pdf_document:
    latex_engine: xelatex
geometry: margin=0.2in
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
# Load config.R
source("config.R") 

# Set root directory using the variable from config
knitr::opts_knit$set(root.dir = data_dir)

# Load libraries
library(MASS)
library(dplyr)
library(data.table, quietly = T)
library(ggplot2)
library(caret)
```

```{r}
# Load Data
# iss_expr <- readRDS("janesick_2023/raw_clean/iss_expr_clean.RDS")
iss_obj_invasive <- readRDS("janesick_2023/processed/iss_obj_invasive.RDS")
shared_genes <- readRDS("janesick_2023/processed/shared_genes.RDS")
```

# Select 2/3 of the shared genes for training
```{r}
# Randomly select 2/3 of the shared genes to serve as the feature pool
# (This mimics selecting a gene panel)
set.seed(lda_params$seed)
train_genes <- sample(shared_genes, size = floor(length(shared_genes) * lda_params$train_prop))

# Save list of training genes
saveRDS(train_genes, file = "janesick_2023/processed/train_genes.RDS")
```

# Filter to Surface and Core cells only
```{r}
# Calculate number of cells before filtering
n_before <- ncol(iss_obj_invasive)

# Get the labels from the dynamically selected method
labels <- iss_obj_invasive@meta.data[[classification_method]]

# Define which classes to KEEP
classes_to_keep <- c("Surface", "Core")

# Create a boolean vector for cells that match the allowed classes
# This automatically removes NAs (as they won't match) and "Other"
cells_to_keep <- !is.na(labels) & (labels %in% classes_to_keep)

# Subset the Seurat object
iss_obj_invasive <- subset(iss_obj_invasive, cells = colnames(iss_obj_invasive)[cells_to_keep])

# Recalculate number of cells after filtering
n_after <- ncol(iss_obj_invasive)
cat(round((n_before - n_after)/n_before, 2)*100, "% cells removed (NAs and 'Other').\n")

# ´Drop unused factor levels (R will still think "Other" is a possible category with 0 cells)
iss_obj_invasive@meta.data[[classification_method]] <- factor(
  as.character(iss_obj_invasive@meta.data[[classification_method]])
)
```


# Normalise the matrix
```{r}
# Manual Log Transformation
# 1. Pull the raw counts
raw_counts <- GetAssayData(iss_obj_invasive, assay = "RNA", layer = "counts")

# 2. log transformation without scaling/centering
log_transformed_counts <- log1p(raw_counts)

# 3. Place into 'data' layer for downstream extraction
iss_obj_invasive <- SetAssayData(
  iss_obj_invasive, 
  layer = "data", 
  new.data = log_transformed_counts
)
```

# Extract normalised counts, add surface_class column
```{r}
inv_tumour_expr <- as.data.frame(t(as.matrix(LayerData(iss_obj_invasive, layer = "data"))))

inv_tumour_expr$surface_class <- iss_obj_invasive@meta.data[, classification_method]
rownames(inv_tumour_expr) <- iss_obj_invasive@meta.data[, 'cell_id']

# use only the surface/core cells (filter others)
inv_tumour_expr <- inv_tumour_expr %>%
  filter(surface_class %in% c("Surface", "Core"))
```


# Split full dataset into training / test datasets (80/20 split)
```{r}
# Configuration for Repeated CV 
n_repeats <- 10       # Number of times to repeat the full 5-fold cycle
n_folds   <- 5        # 5-fold means 80/20 split
set.seed(lda_params$seed)

# Initialise storage
all_predictions <- list()

cat("Starting Repeated", n_folds, "-Fold Cross-Validation (", n_repeats, "repeats )...\n")

# Outer Loop: Repeats 
for (r in 1:n_repeats) {
  
  # Create Folds for this repeat
  # list = TRUE returns indices for training, so we use returnTrain=FALSE to get Test indices
  folds <- createFolds(inv_tumour_expr$surface_class, k = n_folds, list = TRUE, returnTrain = FALSE)
  
  # Inner Loop: K-Folds 
  for (k in 1:n_folds) {
    
    # 1. Split Data
    test_indices <- folds[[k]]
    train_data <- inv_tumour_expr[-test_indices, ]
    test_data  <- inv_tumour_expr[test_indices, ]
    
    # 2. Filter Genes (Feature Selection inside the loop to avoid leakage)
    # Use only the pre-selected 'train_genes' pool
    current_train_subset <- train_data %>% dplyr::select(surface_class, all_of(train_genes))
    
    # Remove zero-variance genes within the training set
    gene_cols <- setdiff(colnames(current_train_subset), "surface_class")
    keep_genes <- sapply(gene_cols, function(gene) {
      var_by_group <- current_train_subset %>%
        group_by(surface_class) %>%
        summarise(var = var(.data[[gene]], na.rm = TRUE), .groups = 'drop')
      any(var_by_group$var > 0)
    })
    active_genes <- names(keep_genes)[keep_genes]
    
    # 3. Fit LDA Model on Training Data
    fit_data <- current_train_subset %>% dplyr::select(surface_class, all_of(active_genes))
    fit_lda_cv <- lda(surface_class ~ ., data = fit_data)
    
    # 4. Predict on Test Data
    predict_data <- test_data %>% dplyr::select(all_of(active_genes))
    pred_obj <- predict(fit_lda_cv, newdata = predict_data)
    
    # 5. Store Predictions
    fold_preds <- data.frame(
      cell_id = rownames(test_data),
      repeat_id = r,
      fold_id = k,
      actual_class = test_data$surface_class,
      predicted_class = pred_obj$class,
      stringsAsFactors = FALSE
    )
    
    all_predictions[[paste0(r, "_", k)]] <- fold_preds
  }
}

# Combine all results
full_results <- do.call(rbind, all_predictions)
```

# Process consensus results
```{r}
# Aggregate predictions per cell
cell_consensus <- full_results %>%
   group_by(cell_id) %>%
   summarise(
     # Fix: Use dplyr::first() explicitly
     actual_class = dplyr::first(actual_class), 
     n_predictions = n(),
     
     # Count how many times it was predicted as Surface
     n_predicted_surface = sum(predicted_class == "Surface"), 
     .groups = 'drop'
   ) %>%
   mutate(
     # Probability of being Surface
     prob_surface = n_predicted_surface / n_predictions,
     
     # Consensus Prediction (> 50% probability)
     consensus_prediction = ifelse(prob_surface > 0.5, "Surface", "Core"),
     
     # Stability: How confident is the model? (1.0 = always same prediction, 0.5 = random)
     stability = pmax(prob_surface, 1 - prob_surface),
     
     # Accuracy check
     is_correct = consensus_prediction == actual_class
   )

cat("Average Stability:", round(mean(cell_consensus$stability), 3), "\n")
cat("Overall Consensus Accuracy:", round(mean(cell_consensus$is_correct), 3), "\n")

saveRDS(cell_consensus, file = "janesick_2023/processed/lda_consensus_results.RDS")
```

# Fit the final global model
```{r}
# 1. Feature selection on full dataset (using train_genes pool)
full_data_subset <- inv_tumour_expr %>% dplyr::select(surface_class, all_of(train_genes))

gene_cols <- setdiff(colnames(full_data_subset), "surface_class")
keep_genes_final <- sapply(gene_cols, function(gene) {
  var_by_group <- full_data_subset %>%
    group_by(surface_class) %>%
    summarise(var = var(.data[[gene]], na.rm = TRUE), .groups = 'drop')
  any(var_by_group$var > 0)
})
final_genes <- names(keep_genes_final)[keep_genes_final]

# 2. Fit Final LDA
fit_lda_final <- lda(surface_class ~ ., data = full_data_subset[, c("surface_class", final_genes)])

saveRDS(fit_lda_final, file = "janesick_2023/processed/fit_lda.RDS")
saveRDS(final_genes, file = "janesick_2023/processed/genes_to_keep.RDS")
```

# plot first 2 linear discriminants
```{r}
# Define figure directory
fig_subdir <- file.path(figs_dir, "0.3.1")
if(!dir.exists(fig_subdir)) dir.create(fig_subdir, recursive = TRUE)

# Calculate LDA values for all cells
lda_values <- predict(fit_lda_final)$x
lda_df <- data.frame(LD1 = lda_values[,1], surface_class = inv_tumour_expr$surface_class)

# Define readable labels
method_labels <- c(
  "surface_class_radius"   = "Radius Definition",
  "surface_class_nn"       = "KNN Definition",
  "surface_class_clusters" = "Unsupervised Clustering"
)
current_label <- method_labels[classification_method]
if(is.na(current_label)) current_label <- classification_method

# Create the plot
p_lda <- ggplot(lda_df, aes(x = LD1, fill = surface_class)) +
  geom_density(alpha = 0.5) +
  theme_minimal() +
  labs(
    title = "LDA Projection (Global Model)", 
    subtitle = paste0("Ground Truth: ", current_label),
    x = "LD1", 
    y = "Density",
    fill = "Region"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10, color = "gray30")
  )

print(p_lda)
ggsave(filename = file.path(fig_subdir, paste0("LDA_density_", classification_method, ".png")), plot = p_lda)
```

# consensus confusion matrix
```{r}
# Create confusion matrix based on the Consensus prediction vs Actual
conf_matrix <- confusionMatrix(
  factor(cell_consensus$consensus_prediction, levels = c("Core", "Surface")),
  factor(cell_consensus$actual_class, levels = c("Core", "Surface"))
)

print(conf_matrix)

capture.output(
  conf_matrix, 
  file = file.path(fig_subdir, paste0("confusion_matrix_consensus_", classification_method, ".txt"))
)
```

# spatial plot of consensus errors
```{r, fig.width=7.87*1.75, fig.height = 6.5*1.75, dpi=300, dev='tiff', out.width='100%'}
# 1. Merge consensus results back with spatial metadata
# We need x_centroid/y_centroid from the original object
meta_coords <- iss_obj_invasive@meta.data %>% 
  dplyr::select(cell_id, x_centroid, y_centroid)

plot_data <- merge(cell_consensus, meta_coords, by = "cell_id")

# 2. Define Classification Status for Plotting
# Logic: If Correct -> "Correct", Else -> "False [Predicted Class]"
plot_data$classification_status <- ifelse(
  plot_data$is_correct, 
  "Correct", 
  paste0("False ", plot_data$consensus_prediction)
)

# 3. Setup Colors
colors <- c("Correct" = "grey80", "False Surface" = "red", "False Core" = "black")

# 4. Plot
p_spatial <- ggplot(plot_data, aes(x = y_centroid, y = x_centroid, color = classification_status)) +
    # Layer 1: Correct (Background)
    geom_point(data = subset(plot_data, classification_status == "Correct"), 
               size = 0.01) +
    # Layer 2: False Surface (Intermediate)
    geom_point(data = subset(plot_data, classification_status == "False Surface"), 
               size = 0.01) +
    # Layer 3: False Core (Top)
    geom_point(data = subset(plot_data, classification_status == "False Core"), 
               size = 0.01) +
    scale_color_manual(values = colors) +
    # Swap axes and reverse Y to match histology orientation
    coord_fixed(ylim = c(3850, 0)) +
    theme_minimal() +
    labs(
      title = "Spatial Map of LDA Classification Errors",
      subtitle = paste0("Based on Consensus of ", n_repeats, "x 5-Fold CV")
    ) +
    guides(color = guide_legend(override.aes = list(size = 3)))

print(p_spatial)

ggsave(
  filename = file.path(fig_subdir, paste0("Spatial_Errors_Consensus_", classification_method, ".png")),
  plot = p_spatial, dpi = 300, width = 8, height = 6
)
```

# plot prediction uncertainty
```{r, fig.width=7.87*1.75, fig.height = 6.5*1.75, dpi=300, dev='tiff', out.width='100%'}
ggplot(plot_data, aes(x = y_centroid, y = x_centroid, color = prob_surface)) +
  geom_point(size = 0.01) +
  scale_color_gradient2(low = "#fac0da", mid = "black", high = "#C90065", midpoint = 0.5,
                        name = "Prob(Surface)") +
  coord_fixed(ylim = c(3850, 0)) +
  theme_minimal() +
  labs(title = "LDA Surface Probability Map", subtitle = "Black = High Uncertainty (Transition Zone)")
```

